Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-11 docs/ms.tex
Update ms.tex

In galaxy--galaxy lensing, since the distortion is so weak, what people
usually do is to stack many lensing signals together. Then they can obain the mean
shear map and infer the mean mass profile of single galaxy or galaxy
cluster. However with the Hierarchical Bayesian method we can avoid this brute averaging
of lensing signal. Instead, we can get the posterior distribution of mass profile for
each lensing system, even though it may have very large uncertainty. Then we
can calculate their statistical properties like galaxy-mass correlation
function via this posterior distribution.

@@

Note that both $\epsilon_{0}$ and $\epsilon_{\ell}$ are complex numbers. So
$|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|$ is the Jacobian
determinant term,which can be calculated numerically from formula
(5).

@@

The prior of $\alpha$ some how depends on the model we choose for
intrinsic ellipticity distribution. When we use the step function
model for P($\epsilon_{0}$), which we'll describe latter. We find that
we need to use a prior on $\alpha$. 
\begin{equation}
p(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})
\end{equation}

@@

One thing to note is that the likelihood of g in patch i only depends
on the shape parameters but not dependent to shear in other patches. Therefore, the
marginalized likelihood of shape parameters is :

@@

Here $\xi$ is a prefactor need to be tuned.

Meanwhile, in order to show the correctness of our method, we also
set up a simulation in which we know the true $P(|\epsilon_{0}||\alpha)$
is a Beta distribution, and thus $\alpha$ is the 2-D parameter (p,q)
of the Beta distribution. We will show the posterior samples using
both of these two methods in next section. Note that for either model
we assume P($\epsilon_{0}$) is isotropic.

>>>>

In galaxy--galaxy lensing, since the distortion is so weak, what people
usually do is to stack many lensing signals together. Then they can obtain the mean
shear map and infer the mean mass profile of single galaxy or galaxy
cluster. However with the Hierarchical Bayesian method we can avoid this brute averaging
of lensing signal. Instead, we can get the posterior distribution of mass profile for
each lensing system, even though it may have very large uncertainty. Then we
can calculate their statistical properties like galaxy-mass correlation
function via this posterior distribution.

@@

Note that both $\epsilon_{0}$ and $\epsilon_{\ell}$ are complex numbers. So
$|\frac{\partial\epsilon_{0}}{\partial\epsilon_{\ell}}|$ is the Jacobian
determinant term, which is calculated numerically from formula
(5).

@@

The prior of $\alpha$ some how depends on the model we choose for
intrinsic ellipticity distribution. When we use the step function
model for P($\epsilon_{0}$), which we'll describe latter, we find that
we need to use a prior regulazier on $\alpha$. 
\begin{equation}
p(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})
\end{equation}

@@

One thing to note is that the likelihood of g in one patch only explicitly depends
on the shape parameters but not dependent to shear in other patches. Therefore, the
marginalized likelihood of shape parameters is :

@@

Here $\xi$ is a prefactor need to be tuned.
Meanwhile, in order to show the correctness of our method, we also
set up a simulation in which we know the true $P(|\epsilon_{0}||\alpha)$
is a Beta distribution, and thus $\alpha$ is the 2-D parameter (p,q)
of the Beta distribution. We will show the posterior samples using
both of these two methods in next section. Note that for either model
we assume P($\epsilon_{0}$) is isotropic.
